%-------------------------
% Resume in Latex
% Author : Siddhanta Choudhury
%------------------------

\documentclass[letterpaper,11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\usepackage{fontawesome}
\usepackage{multicol}
\usepackage[dvipsnames]{xcolor}
\setlength{\multicolsep}{-3.0pt}
\setlength{\columnsep}{-1pt}
\input{glyphtounicode}
\usepackage{ragged2e}

%----------FONT OPTIONS----------
% sans-serif
% \usepackage[sfdefault]{FiraSans}
% \usepackage[sfdefault]{roboto}
% \usepackage[sfdefault]{noto-sans}
% \usepackage[default]{sourcesanspro}

% serif
% \usepackage{CormorantGaramond}
% \usepackage{charter}


\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.6in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1.19in}
\addtolength{\topmargin}{-.7in}
\addtolength{\textheight}{1.4in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \vspace{-4pt}\color{BrickRed}\scshape\raggedright\large\bfseries
}{}{0em}{}[\color{BrickRed}\titlerule \vspace{-5pt}]

% Ensure that generate pdf is machine readable/ATS parsable
\pdfgentounicode=1

%-------------------------
% Custom commands
\newcommand{\resumeItem}[1]{
  \item\small{
    {#1 \vspace{-2pt}}
  }
}

\newcommand{\classesList}[4]{
    \item\small{
        {#1 #2 #3 #4 \vspace{-2pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-2pt}\item
    \begin{tabular*}{1.0\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & \textbf{\small #2} \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubSubheading}[2]{
    \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \textit{\small#1} & \textit{\small #2} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeProjectHeading}[2]{
    \item
    \begin{tabular*}{1.001\textwidth}{l@{\extracolsep{\fill}}r}
      \small#1 & \textbf{\small #2}\\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubItem}[1]{\resumeItem{#1}\vspace{-4pt}}

\renewcommand\labelitemi{$\vcenter{\hbox{\tiny$\bullet$}}$}
\renewcommand\labelitemii{$\vcenter{\hbox{\tiny$\bullet$}}$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0.0in, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

%-------------------------------------------
%%%%%%  RESUME STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%


\begin{document}

%----------HEADING----------
\begin{center}
    \textbf{\Huge \scshape Siddhanta Choudhury} \\ \vspace{1pt}
    \small \textit{\large Aspiring Software Engineer} \\
    \href{tel:+918658607379}{\underline{{+91 8658607379}}} $|$ \href{mailto:siddhanta.c1729@gmail.com}{\underline{siddhanta.c1729@gmail.com}} $|$ 
    Odisha, India $|$
    \href{https://www.linkedin.com/in/siddhanta-choudhury/}{\underline{https://www.linkedin.com/in/siddhanta-choudhury}} $|$
    \href{https://github.com/Sid70}{\underline{https://github.com/Sid70}}
\end{center}

%-----------SUMMARY-----------
\section*{About}
\begin{justify}
{Graduated aspiring Software Engineer proficient in \textbf{Java}, \textbf{C\#}, \textbf{C}, \textbf{C++}, \textbf{Python}, \textbf{PHP}, and \textbf{JavaScript} as well as \textbf{MySQL}. Specializes in \textbf{full-stack development}, particularly skilled with the \textbf{MERN stack} (\textbf{MongoDB}, \textbf{Express.js}, \textbf{React.js}, \textbf{Node.js}). Possesses a strong foundation in \textbf{Data Structures and Algorithms (DSA)}, leveraging technology to innovate, enhance user experiences, and drive project success.}
\end{justify}
\vspace{-18pt}
%-----------EDUCATION-----------
\section{Education}
\resumeSubHeadingListStart
\resumeSubheading
{Sambalpur University Institute of Information Technology, Burla}{Dec 2020 - May 2024}{B.Tech in Computer Science \& Engineering}{CGPA: 7.70/10}
\resumeSubheading
{Vikash Higher Secondary School, Sambalpur}{July 2018 - Apr 2019}{XII - Science}{Percentage: 73\%}
\resumeSubHeadingListEnd

% -----------EXPERIENCE-----------
\section{Internship \& Work Experience}
\resumeSubHeadingListStart
\resumeSubheading
{Central Tool Room \& Training Centre (MSME) Government of India \href{https://drive.google.com/file/d/1yb3f4qoekCHchpvl5ON7zSnXUrwH0Pao/view}{\faExternalLink}}{June 2023 -- June 2023}
{Apprenticeship}{Bhubaneswar, Odisha}
\begin{justify}
\resumeItemListStart
\resumeItem{Mastering core Java programming skills, specializing in JDBC and Swing framework, while demonstrating proficiency in object-oriented programming, data types, control structures, and exception handling.}
\resumeItem{Gaining practical proficiency in Java, JDBC, and Swing through hands-on exercises and project work.}
\resumeItemListEnd
\end{justify}
\resumeSubheading
{Oasis Infobyte \href{https://drive.google.com/file/d/1-nx_JJNNnDPMFFT1Su_ZaUaRVpvAeeM0/view}{\faExternalLink}}{Apr 2023 -- May 2023}
{Project Intern}{Remote}
\begin{justify}
\resumeItemListStart
\resumeItem{Demonstrating proficiency in front-end technologies, encompassing JavaScript, HTML, and CSS, coupled with practical experience in GitHub utilization and deployment via the platform.}
\resumeItem{Acquiring familiarity with vital development tools such as Visual Studio Code and Git, ensuring seamless workflow and efficient collaboration within projects.}
\resumeItem{Executing diverse portfolio projects, ranging from a TO-DO List application to a Calculator and a Tribute Page, showcasing practical application of acquired skills and fostering continuous learning.}
\resumeItemListEnd
\end{justify}
\resumeSubHeadingListEnd

%-----------PROJECTS-----------
\section{Projects}
\vspace{-5pt}
\begin{justify}
\resumeSubHeadingListStart
\resumeProjectHeading{\textbf{CampusNet $|$ \emph{React.Js, Express.Js, MongoDB, Node.Js, Material UI, Git}}}{\href{https://github.com/Sid70/CampusNet}{\underline{Source Code}}}
\resumeItemListStart
\resumeItem{CampusNet is a MERN-based social-media platform for college communities, enabling secure registration, login, and sharing of events, multimedia, educational materials, and job posts.}
\resumeItem{Allows users to manage account with deletion and deactivation options, search others, and receive notifications.}
\resumeItemListEnd
% ***************************************************
\resumeProjectHeading{\textbf{Image Classification App $|$ \emph{React.Js, ml5.js, Git}}}{\href{https://github.com/Sid70/Image-Classification-App}{\underline{Source Code}}}
\resumeItemListStart
\resumeItem{Developed an Image Classification App with ReactJS and integrated the ml5.js API, enabling users to effortlessly categorize images.}
\resumeItemListEnd
% ****************************************************
\resumeProjectHeading{\textbf{School Management System $|$ \emph{HTML, CSS, JavaScript, PHP, BootStrap, MySQL, Git}}}{\href{https://github.com/Sid70/School-Management-System}{\underline{Source Code}}}
\resumeItemListStart
\resumeItem{Comprehensive School Management System with key functionalities like user authentication, registration, profile management, and robust search features.}
\resumeItemListEnd
% ****************************************************
\resumeProjectHeading{\textbf{Bank Management System $|$ \emph{C , Git , GitHub}}}{\href{https://github.com/Sid70/Bank-Mnagement-system-In-C}{\underline{Source Code}}}
\resumeItemListStart
\resumeItem{Built a Bank Management System in C, allowing users to perform various banking operations such as account creation, transaction processing, and account management.}
\resumeItemListEnd
% ****************************************************
\resumeProjectHeading{\textbf{Matrix and Determinant Calculator $|$ \emph{C , Git , GitHub}}}{\href{https://github.com/Sid70/Matrix-and-Determinant-Calculator-in-C}{\underline{Source Code}}}
\resumeItemListStart
\resumeItem{Implemented a Matrix and Determinant Calculator in C, enabling users to perform matrix operations such as addition, subtraction, and multiplication.}
\resumeItem{Incorporated functionalities to calculate determinants and find the inverse of matrices.}
\resumeItem{Utilized C programming language to create a user-friendly interface and ensure efficient calculation of matrix operations.}
\resumeItemListEnd
\vspace{-13pt}
% ****************************************************
\resumeSubHeadingListEnd
\end{justify}
\vspace{-3pt}
%-----------Technical SKILLS-----------
\section{Technical Skills}
\begin{itemize}[leftmargin=0.15in, label={}]
  \item{
        \textbf{Programming Languages}{: Java, C\#, C, C++, JavaScript, Python} \\
        \textbf{Web Development}{: HTML, CSS, JavaScript, PHP, MySQL, MongoDB, React.js, Node.js, Express.js}\\
        \textbf{Frontend Framework}{: React, TailwindCSS, HTML, CSS, Bootstrap, Material UI} \\
        \textbf{Databases}{: MySQL, MongoDB} \\
        \textbf{Developer Tools}{: Postman, Git, GitHub, Visual Studio Code, NetBeans IDE, PyCharm, Code::Blocks} \\
        }
\end{itemize}
\vspace{-15pt}

%-----------Certifications-------------
\section{Certifications}
\resumeSubHeadingListStart
% *******************************************
\resumeSubheading{Full Stack Web Development \href{https://trainings.internshala.com/view_certificate/9B3A0AA2-A803-BF47-11F5-14676C3F5113/FA1CD614-1868-1D86-30C0-C723850D99F9/}{\faExternalLink}}{}{}{}
\resumeItemListStart
\vspace{-4mm}
\resumeItem{An 8-week online training on Web Development. The training consisted of HTML, CSS, Bootstrap, DBMS, PHP, JS, React, and Final Project modules.}
\resumeItemListEnd
% *******************************************
\resumeSubheading{Programming with C and C++ \href{https://trainings.internshala.com/view_certificate/F7A8BF3B-ACC5-C888-E3D4-4B60C3284DE5/8B7122CB-E39D-A3BC-50C9-DDDFE471AC00/}{\faExternalLink}}{}{}{}
\resumeItemListStart
\vspace{-4mm}
\resumeItem{Trained in C and C++ programming, with a focus on Object-Oriented Programming. Developed a Cricket Game Application as part of the training.}
\resumeItemListEnd
\resumeSubHeadingListEnd

% ------------------- Achievements --------------
\section{Achievements}
\resumeSubHeadingListStart
% *******************************************
\resumeSubheading{Participation in Hacktoberfest \href{https://www.holopin.io/@sid70}{\faExternalLink}}{\hfill {Oct 2022}}{}{}
\resumeItemListStart
\vspace{-4mm}
\resumeItem{Contributed to and completed 5 pull requests during Hacktoberfest 2022.}
\resumeItem{Earned exciting goodies and badges as a result.}
\resumeItemListEnd
% *******************************************
\resumeSubheading{Winner of Bits nd Bytes Techwiz \href{https://unstop.com/api/certificate/12a81d6b-87d1-4cd1-8b92-b486f11b2dc1}{\faExternalLink}}{Jan 2022}{}{}
\resumeItemListStart
\vspace{-4mm}
\resumeItem{Secured the first position in 'Bits nd Bytes', a knowledge-boosting computer basics and coding quiz competition.}
\resumeItem{Organized by CodeCircle, part of the Innovation Club at SUIIT.}
\resumeItemListEnd
\resumeSubHeadingListEnd


% Languages ----------------------------------
\section{Languages}
\begin{itemize}[leftmargin=0.15in, label={}]
  \item{
        \textbf{English:}{ Professional Proficiency} \\
        \textbf{Hindi}{: Professional Proficiency}\\
        \textbf{Odia}{: Native Proficiency}\\
        }
\end{itemize}

\end{document}
